---
output:
  html_document: default
---

```{r echo=FALSE}
options(crayon.enabled = TRUE, tibble.max_extra_cols = 10)

library(knitr)
opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, autodep = TRUE,
               dev = 'png', fig.width = 10, fig.height = 10,
               cache.lazy = FALSE, fig.align = "center")
knit_hooks$set(
  hide_button = function(before, options, envir) {
    if (is.character(options$hide_button)) {
      button_text = options$hide_button
    } else {
      button_text = "Show solution"
    }
    block_label <- paste0("hide_button", options$label)
    if (before) {
      return(paste0(sep = "\n",
                    '<button class="btn btn-danger" data-toggle="collapse" data-target="#', block_label, '"> ', button_text, ' </button>\n',
                    '<div id="', block_label, '" class="collapse">\n'))
    } else {
      return("</div><br />\n")
    }
  },
  output = function(x, options){
    x <- gsub(x, pattern = "<", replacement = "&lt;")
    x <- gsub(x, pattern = ">", replacement = "&gt;")
    paste0(
      "<pre class=\"r-output\"><code>",
      fansi::sgr_to_html(x = x, warn = TRUE, term.cap = "256"),
      # ansistrings::ansi_to_html(text = x, fullpage = FALSE),
      "</code></pre>"
    )
  }
)
options(width = 100)
```

# Voting geography example


## Install packages

```{r eval=FALSE}
# install.packages("metacoder")
# install.packages("readr")
```

## Load packages

```{r}
library(readr)
library(metacoder)
library(dplyr)
```


## Introduction

Although `metacoder` and `taxa` have been designed for use with taxonomic data, any data that can be assigned to a hierarchy can be used. 
To demonstrate this, we have used metacoder to display the results of the 2016 Democratic primary election. 

## Read in data

We will use the `readr` package to read in the data.
You can download the data [here](primary_results.csv).

```{r}
raw_data <- read_csv("primary_results.csv")
raw_data
```

## Create and parse classifications

Instead of have taxonomic ranks in columns, this data has regions in columns, but its the same idea.

```{r}
obj <- parse_tax_data(raw_data,
                      class_cols = c("country", "region", "division", "state", "county"),
                      named_by_rank = TRUE)
obj
```

## Get canidate vote counts

We have now need to sum the data for geographic region.

```{r}
obj$data$totals <- obj %>%
  filter_obs("tax_data", candidate == "Bernie Sanders") %>%
  calc_taxon_abund("tax_data", cols = "votes", out_names = "bernie")
obj$data$totals <- obj %>%
  filter_obs("tax_data", candidate == "Hillary Clinton") %>%
  calc_taxon_abund("tax_data", cols = "votes", out_names = "hillary") %>%
  left_join(obj$data$totals)
obj <- mutate_obs(obj, "totals", total = bernie + hillary)
```

## Get top counties

I will get a list of the "taxon" IDs for the county in each state with the most votes.

```{r}
top_counties <- unlist(subtaxa_apply(obj, subset = taxon_ranks == "state", value = "total",
                                     function(x) names(x[which.max(x)])))
```

## Plotting results

```{r}
obj %>%
  heat_tree(node_size = total,
            node_size_range = c(0.0002, 0.06),
            node_color = (hillary - bernie) / total * 100,
            edge_label = ifelse(taxon_ids %in% top_counties | n_supertaxa <= 3, taxon_names, ""),
            edge_label_size_trans = "area",
            edge_label_size_range = c(0.008, 0.025),
            node_color_range = c("#a6611a", "lightgray", "#018571"),
            node_color_interval = c(-50, 50),
            edge_color_range = c("#a6611a", "lightgray", "#018571"),
            edge_color_interval = c(-50, 50),
            node_color_axis_label = "Clinton               Sanders",
            node_size_axis_label = "Total votes",
            repel_labels = FALSE,
            output_file = "voting.png")
```
